AHABus \& FCORE:\\Modular Bus for High-Altitude Balloon Missions

### 2017-04-13 chapters/03-methodology.tex
pre-discussion
Change bus status semantics

The health of each subsystem is stored globally, and each system can indicate
an issue by modifying its entry. There are four health states that subsystems
can have, represented each by a single ASCII character: booting (B), up (U),
recovering (R) and down (D). Each system is flagged as booting on startup.
Payloads are flagged as recovering if the last attempt to poll their data
failed, and down if more than five attempts to communicate failed in a row.
the \acrshort{gnss} subsystem is flagged as recovering if no valid position
fix was received from the receiver, and down if the received messages were not
parsed correctly.

@@

\subsection{Mission Design and Configuration Files}
\label{sssec:conf-file}

@@

>>>>

The health of each subsystem is stored globally, and each system can indicate
an issue by modifying its entry. There are four health states that subsystems
can have, represented each by a single ASCII character: booting (B), up (U),
recovering (R) and down (D). Each system is flagged as booting on startup.
Payloads are flagged as recovering if the payload attempted to transmit more
data than it is allowed, and down if it failed to respond to polling. the
\acrshort{gnss} subsystem is flagged as recovering if no valid position fix was
received from the receiver, and down if the received messages were not parsed
correctly.

@@

\subsection{Mission Design and Configuration Files}
\label{ssec:conf-file}

@@

Each test involved having the prototype platform run for ten minutes in normal
conditions, an attempting to decode packets using ground segment software.

### 2017-04-13 chapters/05-discussion.tex
Change bus status semantics

As a software platform, the \acrshort{ahabus} prototype fulfils most of its
goals: the flight \acrshort{fcore} was complete enough to support full-flight
simulations, manage the bus, \acrshort{gnss} and radio communications without
failure. During the testing phase, no major software design error were found,
and the only instances where failures were found to be caused by the flight
software itself. Though quite cumbersome to work with, and lacking in
documentation, the \acrshort{fcore} configuration tool discussed in section
\ref{sssec:conf-file} proved reliable, and the resulting \acrshort{fcore} builds
did not suffer from erroneous bandwidth usage.

@@

One solution to this issue would be the use of an end-of-frame marker instead,
and to reject frames that are shorter than 256 bytes. However, this approach
would be challenging to implement in the context of the \acrshort{ahabus} radio
protocol. Because the end marker value might occur in the frame's content, it
must be escaped so that the decoder does not interpret a content byte as the
frame end. This can be achieved through \textit{byte stuffing}: an escape value
is chosen, and any end marker or escape value that occurs in the content must
be preceded by the escape value. The use of \acrshort{fec} in the protocol
further complicates the issue: the \acrlong{ecc} would have to be escaped too,
making frames impossible to error-correct before the escaped bytes have been
resolved by the decoder. This means that a single corrupted escape byte in a
received frame would prevent the frame from being corrected at all, even if the
number of invalid bytes is inferior to the \acrshort{fec} algorithm limit.

>>>>

As a software platform, the \acrshort{ahabus} prototype fulfils most of its
goals: the flight \acrshort{fcore} was complete enough to support full-flight
simulations, manage the bus, \acrshort{gnss} and radio communications without
failure. During the testing phase, no major software design error were found,
and the only instances where failures were found to be caused by the flight
software itself. Though quite cumbersome to work with, and lacking in
documentation, the \acrshort{fcore} configuration tool discussed in section
\ref{ssec:conf-file} proved reliable, and the resulting \acrshort{fcore} builds
did not suffer from erroneous bandwidth usage.

@@

One solution to this issue would be the use of an end-of-frame marker instead,
and to reject frames that are shorter than 256 bytes. However, this approach
would be challenging to implement in the context of the \acrshort{ahabus} radio
protocol. Because the end marker value might occur in the frame's content, it
must be escaped so that the decoder does not interpret a content byte as the
frame end. This can be achieved through \textit{byte stuffing}: an escape value
is chosen, and any end marker or escape value that occurs in the content must
be preceded by the escape value. The use of \acrlong{fec} in the protocol
further complicates the issue: the \acrlong{ecc} would have to be escaped too,
making frames impossible to error-correct before the escaped bytes have been
resolved by the decoder. This means that a single corrupted escape byte in a
received frame would prevent the frame from being corrected at all, even if the
number of invalid bytes is inferior to the \acrshort{fec} algorithm limit.
